Technical Report

### 2017-09-28 fully-abstract-comp/technical-report.tex
adjusted splice semantics slightly

                                  \Phi(r_2) = ((\perm,\lin),\baddr_2,\eaddr_2,\aaddr_2) \tand \\
                                  \Phi(r_3) = ((\perm,\lin),\baddr_3,\eaddr_3,\_) \tand \\

@@

                                  c = ((\perm,\lin),\baddr_2,\eaddr_3,\aaddr_2) \tand\\

@@

                                  \Phi(r_2) = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,2},\sigma} \tand \\
                                  \Phi(r_3) = \seal{\lin,\sigma_{\baddr,3},\sigma_{\eaddr,3},\_} \tand \\

@@

                                  \Phi(r_2) = \stkptr{\perm,\baddr_2,\eaddr_2,\aaddr_2} \tand \\

@@

                                  c = \stkptr{\perm,\baddr_2,\eaddr_3,\aaddr_2} \\

@@

\noindent\textbf{call}\\
\lau{19-09-2017: How do we get the $\sigma_?$ for the return pointers? It should be in memory somewhere.}
\lau{19-09-2017: In which cases do we have undefined here?}
This instruction assumes that the current address of the stack pointer, $\aaddr_\stk$, points to the first free address of the stack. We assume a seal assignment function $\sealAss{}$ that given an address assigns a seal.\lau{25-09-2017: This will need some more explanation - namely, there should be some relationship between the available seals and this function (I also need to think more about the specifics of this).}
\begin{align*}
  \sem{\scall{\src{r_1}}{\src{r_2}}}(\Phi) = & 
                                               \begin{cases}
                                                 \Phi'
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{rl}
                                                   &\updReg{r_1}{w_1} \\
                                                        &\updReg{r_2}{w_2} \\
                                                        &\updReg{\pcreg}{c_1}\\
                                                        &\updReg{\rdata}{c_2}\\
                                                        &\updReg{\rstk}{c_\stk}\\
                                                        &\updReg{r_{\var{ret,c}}}{\retptrc(\sigma_?)}\\
                                                        &\updReg{r_{\var{ret,d}}}{\retptrd(\sigma_?)}
                                                 \end{array}
                                                 & 
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{l}
                                                   \Phi(r_1) = \sealed{c_1,\sigma_1} \tand \\
                                                   \Phi(r_2) = \sealed{c_2,\sigma_2} \tand \\
                                                   \sigma_1 = \sigma_2 \tand \\
                                                   \nonExec{c_2} \tand\\
                                                   \Phi = (\mem,\reg,\stk,\ms_\stk) \tand\\
                                                   \Phi(\rstk) = \stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk} \tand \\
                                                   \baddr_\stk \leq \aaddr_\stk < \eaddr_\stk \tand \\
                                                   \ms_{\stk,\priv} = \ms_\stk |_{[\baddr_\stk,\aaddr_\stk]}\update{\aaddr_\stk}{\eaddr_\stk} \tand\\
                                                   \ms_{\stk,\var{rest}} = \ms_\stk|_{[\aaddr_\stk + 1,\eaddr_\stk]} \tand \\
                                                   c_\stk = \stkptr{\aaddr_\stk+1,\eaddr_\stk,\aaddr_\stk+1} \tand \\
                                                   \Phi(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                                   \opc = ((\perm,\lin),\baddr,\eaddr,\aaddr+\calllen) \tand \\
                                                   \stk' = (\opc,\ms_{\stk,\priv},\aaddr_\stk) :: \stk \tand\\
                                                   \Phi' = (\mem,\reg,\stk',\ms_{\stk,\var{rest}})\tand\\
                                                   \mem(\baddr) = \seal{\_,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}\tand\\
                                                   \sigma_\baddr \leq \sigma_? \leq \sigma_\eaddr \tand\\
                                                   \sigma_? = \sealAss{a} \tand\\
                                                   w_1 = \linCons{\Phi(r_1)} \tand \\
                                                   w_2 = \linCons{\Phi(r_2)}
                                                 \end{array}
                                               \end{cases}
\end{align*}

@@

One way to solve this is to make it publicly known what the end address of the stack is and always check that we receive a part of the stack that goes all the way to the end. In the above example (using the stack parts in parenthesis) this would cause the sequence of calls to fail the second time we are called, because we do not receive a stack that goes all the way to the top of the stack.

>>>>

                                  \Phi(r_2) = ((\perm,\lin),\baddr_2,\eaddr_2,\_) \tand \\
                                  \Phi(r_3) = ((\perm,\lin),\baddr_3,\eaddr_3,\aaddr_3) \tand \\

@@

                                  c = ((\perm,\lin),\baddr_2,\eaddr_3,\aaddr_3) \tand\\

@@

                                  \Phi(r_2) = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,2},\_} \tand \\
                                  \Phi(r_3) = \seal{\lin,\sigma_{\baddr,3},\sigma_{\eaddr,3},\sigma} \tand \\

@@

                                  \Phi(r_2) = \stkptr{\perm,\baddr_2,\eaddr_2,\_} \tand \\

@@

                                  c = \stkptr{\perm,\baddr_2,\eaddr_3,\aaddr_3} \\

@@

\noindent\textbf{call}\\
\lau{19-09-2017: How do we get the $\sigma_?$ for the return pointers? It should be in memory somewhere.}
\lau{19-09-2017: In which cases do we have undefined here?}
This instruction assumes that the current address of the stack pointer, $\aaddr_\stk$, points to the first free address of the stack. We assume a seal assignment function $\sealAss{}$ that given an address assigns a seal.\lau{25-09-2017: This will need some more explanation - namely, there should be some relationship between the available seals and this function (I also need to think more about the specifics of this).}
\begin{align*}
  \sem{\scall{\src{r_1}}{\src{r_2}}}(\Phi) = & 
                                               \begin{cases}
                                                 \Phi'
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{rl}
                                                   &\updReg{r_1}{w_1} \\
                                                        &\updReg{r_2}{w_2} \\
                                                        &\updReg{\pcreg}{c_1}\\
                                                        &\updReg{\rdata}{c_2}\\
                                                        &\updReg{\rstk}{c_\stk}\\
                                                        &\updReg{r_{\var{ret,c}}}{\retptrc(\sigma_?)}\\
                                                        &\updReg{r_{\var{ret,d}}}{\retptrd(\sigma_?)}
                                                 \end{array}
                                                 & 
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{l}
                                                   \Phi(r_1) = \sealed{c_1,\sigma_1} \tand \\
                                                   \Phi(r_2) = \sealed{c_2,\sigma_2} \tand \\
                                                   \sigma_1 = \sigma_2 \tand \\
                                                   \nonExec{c_2} \tand\\
                                                   \Phi = (\mem,\reg,\stk,\ms_\stk) \tand\\
                                                   \Phi(\rstk) = \stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk} \tand \\
                                                   \baddr_\stk < \aaddr_\stk \leq \eaddr_\stk \tand \\
                                                   \ms_{\stk,\priv} = \ms_\stk |_{[\aaddr_\stk,\eaddr]}\update{\aaddr_\stk}{\eaddr_\stk} \tand\\
                                                   \ms_{\stk,\var{rest}} = \ms_\stk|_{[\baddr,\aaddr_\stk - 1]} \tand \\
                                                   c_\stk = \stkptr{\baddr,\aaddr_\stk-1,\aaddr_\stk-1} \tand \\
                                                   \Phi(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                                   \opc = ((\perm,\lin),\baddr,\eaddr,\aaddr+\calllen) \tand \\
                                                   \stk' = (\opc,\ms_{\stk,\priv},\aaddr_\stk) :: \stk \tand\\
                                                   \Phi' = (\mem,\reg,\stk',\ms_{\stk,\var{rest}})\tand\\
                                                   \mem(\baddr) = \seal{\_,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}\tand\\
                                                   \sigma_\baddr \leq \sigma_? \leq \sigma_\eaddr \tand\\
                                                   \sigma_? = \sealAss{a} \tand\\
                                                   w_1 = \linCons{\Phi(r_1)} \tand \\
                                                   w_2 = \linCons{\Phi(r_2)}
                                                 \end{array}
                                               \end{cases}
\end{align*}

@@

One way to solve this problem is to make the "top addess" of the stack known. There are many ways to do this, but we have chosen to do the following:
\begin{itemize}
\item The stack grows downwards, so the ``last address'' of the stack is the base address of the initial stack capability.
\item The base address of the stack capability is a fixed address, so in the semantice, it will be expressed as a constant that is publicly known.
\end{itemize}
